Checkpoint 3

### 2020-04-22 Checkpoint3.Rmd
analysis

---
title: "Checkpoint 3"
author: "Quinn Rafferty, Ferderico Chung, Sofia Pozsonyiova, Will Madairy"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_document:
    toc:true
    toc_float:true
---

@@

$$

$$

>>>>

---
title: "Checkpoint 3"
author: "Quinn Rafferty, Sofia Pozsonyiova, Will Madairy, Federico Chung"
date: ""
output: 
  html_document:
    toc: true
    toc_float: true
---

@@

```{r}
# Take a sub-sample of the data
set.seed(84735)
test1 <- Finaldata %>% 
  select(mean_KungFluInterest, percent_republican2016, percent_asian, StateColor) %>%
  na.omit() %>% 
  sample_n(500)

names(test1) <- tolower(names(test1))

test1
```

```{r}
set.seed(454)
building_mod <- stan_glm(
  mean_kungfluinterest ~ percent_republican2016 + percent_asian +statecolor, 
  data = test1, 
  family = gaussian, 
  chains = 4, iter = 10000
)
```

```{r}
mcmc_trace(building_mod)
mcmc_dens_overlay(building_mod)
```

```{r}
pp_check(building_mod)
```

```{r}
summary_building_mod <- summary(building_mod)

head(as.data.frame(summary_building_mod),-2)
```

```{r}
prediction_summary_data <- function(y, yrep, prob_inner = 0.5, prob_outer = 0.95){
  # Calculate summary statistics of simulated 
  # posterior predictive models for each case
  l_outer <- function(x){quantile(x, (1-prob_outer) / 2)}
  l_inner <- function(x){quantile(x, (1-prob_inner) / 2)}
  u_inner <- function(x){quantile(x, 1 - (1-prob_inner) / 2)}
  u_outer <- function(x){quantile(x, 1 - (1-prob_outer) / 2)}
  df <- data.frame(yrep) %>% 
    summarize_all(list(mean, sd, median, mad, l_outer, l_inner, u_inner, u_outer)) %>%
    unlist() %>% 
    matrix(., length(y), 8) %>% 
    data.frame()
  names(df) <- c("post_mean", "post_sd", "post_median", "post_mad", "l_outer", "l_inner", "u_inner", "u_outer")
  data.frame(cbind(y, df))
}

prediction_summary <- function(y, yrep, prob_inner = 0.5, prob_outer = 0.95){
  # This function summarizes the predictions across all cases
  pred_data <- prediction_summary_data(y, yrep, prob_inner = prob_inner, prob_outer = prob_outer) %>% 
    mutate(error = y - post_median) %>% 
    mutate(error_scaled = error / post_mad) %>% 
    mutate(within_inner = (y >= l_inner) & (y <= u_inner)) %>% 
    mutate(within_outer = (y >= l_outer) & (y <= u_outer))

  pred_summary <- pred_data %>% 
    summarize(mae = median(abs(error)), 
      mae_scaled = median(abs(error_scaled)),
      within_inner = mean(within_inner),
      within_outer = mean(within_outer)
    )
  names(pred_summary)[3] <- paste0("within_", prob_inner*100)
  names(pred_summary)[4] <- paste0("within_", prob_outer*100)

  pred_summary
}
```

```{r}
preds <- posterior_predict(building_mod,newdata = test1) # Ask Alicia 
prediction_summary(y = test1$mean_kungfluinterest, yprep = preds)

```
